### 2014-07-17 ResearchNotes.Rmd
Editing and formating done.  On to purging forecasts of what I don't need.

>>>>

Format the Loads data.

```{r}
summary(Loads)
```
Those just look like column numbers.  I want hour 19, X.20 and the date.

```{r}
KeyLoads<-Loads[,c(1, 20)]
names(KeyLoads)<-c("Date","Hour19")
#convert to numeric
KeyLoads$Hour19<-as.numeric(as.character(KeyLoads$Hour19))

#convert to ct Date
KeyLoads$Date<-as.POSIXct(KeyLoads$Date,format='%m/%d/%Y')
summary(KeyLoads)
#clean up loads
rm(Loads)
```

Clean up forecasts

```{r}
KeyForecasts<-Forecasts[,c(1,2,21)]
names(KeyForecasts)<-c("EvalTime","Date","Forecast")

#Fixing time
KeyForecasts$Date<-as.POSIXct(KeyForecasts$Date,format='%m/%d/%Y')
KeyForecasts$EvalTime<-as.POSIXlt(KeyForecasts$EvalTime,format="%m/%d/%Y %H:%M:%S")
summary(KeyForecasts)
#why are there two of each date?  Because they do day ahead and two day ahead.
```

Edit the forecasts so that we have only the earliest day ahead forecast.

```{r}

```
